\documentclass[a4paper,12pt]{article}
%\usepackage[ngerman]{babel}
\usepackage{graphicx}
\usepackage{epsfig}
\setlength{\parindent}{0pt}

\usepackage[colorlinks = true,
             linkcolor = black,
             urlcolor  = blue,
             citecolor = blue,
anchorcolor = blue]{hyperref}
\urlstyle{sf}

\usepackage{bbm}

\usepackage{fancyhdr}
\usepackage{color}
\usepackage{soul}
  \setstcolor{red} 



\newcommand{\comment}[1]{}


\setlength{\textheight}{23.82cm}
\setlength{\textwidth}{15.42cm}
\setlength{\oddsidemargin}{0.2cm}
\setlength{\topmargin}{-0.45cm}
\setlength{\headsep}{1ex}
\setlength{\headheight}{3ex}
\setlength{\footskip}{4ex}
\setlength{\parindent}{0em}
\renewcommand{\baselinestretch}{1.1}

% \pagestyle{fancy}
% 
% \fancyhead{}
% \fancyhead[LE,RO]{\large{\bf Dr Werner Bauer}}
% \fancyfoot{}
% 
% \newcommand{\incl}[1]{{\color{blue}#1}}
% \newcommand{\tobemod}[1]{{\color{red}#1}}

\usepackage{soul}
  \setstcolor{blue} 

\begin{document}
\begin{flushright}
\textbf{Dr Werner Bauer}\\
School of Mathematics and Physics\\
University of Surrey\\
Guildford, GU2 7XH\\
\href{mailto:w.bauer@surrey.ac.uk}{\texttt w.bauer@surrey.ac.uk}\
\end{flushright}


\vspace{-0.5em}

\begin{flushleft}
Journal of Computational Physics\\
Editorial Board
\end{flushleft}

\vspace{-0.5em}

\begin{flushright}
Guildford, October 2025
\end{flushright}

\vspace{1.5em}



{\bf Significance and Novelty}


\vspace{1.5em}
Dear board of Editors,


\vspace{0.8em}

please find attached our manuscript entitled ``Fully implicit timestepping methods for the rotating shallow water equations'' for consideration for publication in Journal of Computational Physics.

\vspace{0.8em}

In this manuscript, we introduce a novel iterative solver strategy for
fully implicit Runge-Kutta (IRKs) time integrators for the rotating
shallow water equations, discretised using compatible finite element
methods. Benchmarking against the widely used implicit-explicit (IMEX)
ARK2 scheme of Giraldo et al. (2013), we demonstrate that our scheme
is close to this IMEX scheme for comparable accuracy and can provide
faster wallclock times if less accuracy is needed.

\vspace{0.8em}

Our approach is significant because it provides a novel approach to
solving implicit RK schemes in the context of geophysical fluid dynamics.
IRKs allow us to extend energy conserving spatial discretization to the full
discrete scheme, they avoid errors due to the splitting of the equations in IMEX methods, and they are usually more stable.

Therefore, we hope that our manuscript is of interest for the readers of JCOMP.

\vspace{0.8em}

We confirm that this manuscript describes original work and is not under consideration by any other journal. 
Both authors approved the manuscript and this submission.

\vspace{0.8em}

Thank you for considering our manuscript for review. We appreciate your time and look forward to hearing 
from you. 

\vspace{1.5em}

Kind regards,

\vspace{1.5em}

Werner Bauer,  \\
%Department of Mathematics, Imperial College London, London, UK\\
% \href{mailto:w.bauer@imperial.ac.uk}{\texttt w.bauer@imperial.ac.uk}

\vspace{-0.5em}

Colin J. Cotter
%Department of Mathematics,
(Imperial College London, London, UK,
\href{mailto:colin.cotter@imperial.ac.uk}{\texttt colin.cotter@imperial.ac.uk})

%
% \vspace{0.5em}
%
% Beth Wingate\\
% College of Engineering, Mathematics and Physical Sciences, University of Exeter, UK\\
% \href{mailto: b.wingate@exeter.ac.uk}{\texttt b.wingate@exeter.ac.uk}



% \begin{enumerate}
%  \item     An introduction stating the title of the manuscript and the journal to which you are submitting.
%  \item     The reason why your study is important and relevant to the journal’s readership or field.
%  \item     The question your research answers.
%  \item     Your major experimental results and overall findings.
%  \item     The most important conclusions that can be drawn from your research.
%  \item   A statement that the manuscript has not been published and is not under consideration for publication in any other journal.
%  \item    A statement that all authors approved the manuscript and its submission to the journal.
%  \item   Any other details that will encourage the editor to send your manuscript for review.
% \end{enumerate}



\end{document}
